A New Metropolis-Hastings Test for Fast Minibatch MCMC Inference and Optimization

### 2016-05-16 nips_2016.tex
1st exp

We start with a simple mixture of Gaussians.

@@

{\color{blue}
Daniel: I can borrow some of the description from the Appendix into here, but I need to know what we
are testing. What is the purpose of this experiment? What do we want to show? Once I know that,
writing this part will be easier, and for the Gaussian case in particular, the experiment is pretty
simple and can be run on short notice.

For additional details, see Appendix~\ref{app:gaussian}.
}

\subsection{Logistic Regression}\label{ssec:logistic}

\begin{figure}[ht]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will be a sequence of images for logistic regression.}
\end{figure}

>>>>

We start with a simple mixture of Gaussians, which has the tied means:

\[
\theta_1 \sim N(0, \sigma_1^2); \theta_2 \sim N(0, \sigma_2^2); x_i \sim \frac{1}{2}N(\theta_1, \sigma_x^2) + \frac{1}{2} N(\theta_2, \sigma_x^2)
\]
where $\sigma_1^2 = 10, \sigma_2^2 = 1$ and $\sigma_x^2=2$. 200 data points are generated from the model with $\theta_1 = 0$ and $\theta_2 = 1$. The theoretical posterior distribution can be seen in Fig.~3a. We use random walk as the proposer. We set the step size 0.1 as a constant. We compare three scenarios: with our mini-batch MH testing (see Fig.~3b), without our mini-batch MH testing (see Fig.~3c), and with the standard MH testing (see Fig.~3d).

@@

From the figures above, we find that with the help of our mini-batch MH testing we can obtain the sampled distribution which are very close to target one. We feature draw our estimation of standard derivation of $X_{\rm norm}$ over iterations, see Fig.~3e. We find with even constant step size, the standard derivation decreases, because the gradient of posterior distribution declines and make the scale of $\Delta'$ deminished when the sampled point is apporching MAP. Thus, the error our transition kernel will declines with even constant step size as discribed in Sect.~ 4.
\subsection{Logistic Regression}\label{ssec:logistic}
In this experiment, we use logistic regression to classify the MNIST dataset. For similification, we only train the binary classifer for digits 1 vs 7. The dataset consisted of 12007 training data and 1000 testing data. Similarly, we use random walk as the proposer. We compare our mini-batch MH testing with the adaptive mini-batch MH testing. Figure 4 shows the loglikelihood value and perdiction accuracy over training process. Since the adaptive MH testing method needs to increase the mini-batch size adaptively, we use the cumulative number of data instance each algorithm consumes as the horizontal axis.
\begin{figure}[ht]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will be a sequence of images for logistic regression.}
\end{figure}
